IN FOCUS \\ Natural history matters: how biological constraints shape diversified interactions in pollination networks

### 2016-07-06 ms_infocus.tex
Added Fig 2.
Edits to final part. Added refs.

Th trait matching between HPL and EFL is crucial in this type of interaction and determines its outcome in terms of fitness for both partners. Nilsson \citep{Nilsson:1988} demonstrated experimentally that shortening the nectary tube of long-spurred corollas decreased both seed set and pollinia removal for \textit{Platanthera} orchids. Further experimental evidence has been provided for long-tongued nemestrinid flies pollinating long-tubed irises in South Africa, where increased mismatch decreases both plant fitness and the nectar extraction efficiency of the pollinators \citep{Pauw:2009}. Sazatornil \textit{et al.} extend those results to the scale of the whole moth-plant assemblage and demonstrate that trait matching successfully predicts the diversity of interactions recorded. Interestingly enough, the interaction patterns in two local assemblages from ecotone areas of the Chaco woodland-Yungas montane rain forest transition are better fitted by a neutral model where pairwise interactions are driven by probability of interspecific encounter. Yet Sazatornil \textit{et al.} did not include the morphological difference for parameter estimation when interactions were not recorded. Thus the test of the mismatch hypothesis implicitly includes forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually means a forbidden link. Furthermore,  a fraction of unobserved interactions was likely caused by phenological uncoupling between flowering and hawkmoth activity phenophases \citep{BasJor:2014,Sazatornil:2016}. In any case the mismatch hypothesis somehow captures the fact that a fraction of the unobserved interactions in these hawkmoth/flower assemblages is due to extreme phenotypic mismatch (i.e., size-related forbidden links) \citep{Sazatornil:2016}.

% Explain the biological basis of mismatch using Fig 2 and Arditti

% Forbidden links background.

Sazatornil et al. approach would be most useful for proper tests of coevolutionary hypotheses in hawkmoth/flower assemblages (and plant-animal mutualisms in general): assessing match/mismatch patterns for every possible pairwise interaction among partners within complex webs of interaction where multiple life-history attributes may contribute biological reasons to expect forbidden links. The morphological match hypothesis is not the only mechanism to explain patterns of hawkmoth–plant interactions, where other life-history limitations may operate generating forbidden links, e.g., phenological mismatches (for example in the case of long-distance or elevational migratory hawkmoths), energetic constraints due to nectar availability/foraging costs balances, etc.

@@

@@

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms, a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: Andrea Cocucci. An sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=14cm]{Fig1}
  \end{center}
\end{figure}
%---------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MS NOTES
\begin{comment}
\bibitem{Borrell:2005}
Borrell, B. (2005) Long tongues and loose niches: Evolution of euglossine bees and their nectar flowers. Biotropica, 37, 664–669.

\bibitem{More:2012}
Mor\'e, M., Amorim, F.W., Benitez-Vieyra, S., Medina, A.M., Sazima, M. \& Cocucci, A.A. (2012) Armament imbalances: match and mismatch in plant-pollinator traits of highly specialized long-spurred orchids. PLoS ONE, 7, e41878.

>>>>

Th trait matching between HPL and EFL is crucial in this type of interaction and determines its outcome in terms of fitness for both partners. Nilsson \citep{Nilsson:1988} demonstrated experimentally that shortening the nectary tube of long-spurred corollas decreased both seed set and pollinia removal for \textit{Platanthera} orchids. Further experimental evidence has been provided for long-tongued nemestrinid flies pollinating long-tubed irises in South Africa, where increased mismatch decreases both plant fitness and the nectar extraction efficiency of the pollinators \citep{Pauw:2009}. Sazatornil \textit{et al.} extend those results to the scale of the whole moth-plant assemblage and demonstrate that trait matching successfully predicts the diversity of interactions recorded. Interestingly enough, the interaction patterns in two local assemblages from ecotone areas of the Chaco woodland-Yungas montane rain forest transition are better fitted by a neutral model where pairwise interactions are driven by probability of interspecific encounter. Yet Sazatornil \textit{et al.} did not include the morphological difference for parameter estimation when interactions were not recorded. Thus the test of the mismatch hypothesis implicitly includes forbidden links effects: a full mismatch of corolla tube/proboscis lengths actually means a forbidden link. Furthermore,  a fraction of unobserved interactions was likely caused by phenological uncoupling between flowering and hawkmoth activity phenophases \citep{BasJor:2014,Sazatornil:2016}. In any case the mismatch hypothesis somehow captures the fact that a fraction of the unobserved interactions in these hawkmoth/flower assemblages is due to extreme phenotypic mismatch, i.e., size-related forbidden links \citep{Sazatornil:2016}; also see \citep{VizentinBugoni:2014} for evidences with hummingbird-flower interactions.

% Forbidden links background.
% Explain the biological basis of mismatch using Fig 2 and Arditti
Forbidden links represent a family of causes for not observing specific interactions when sampling diversified plant-animal interaction networks, and stem on biological causes deeply linked to the fascinating natural history details of these interactions \citep{BasJor:2014}. The raw material for phenotypic mismatches in the specific case of hawkmoth-flower interactions is the extreme variability of the two pivotal traits determining their outcomes: proboscis length and corolla/spur or nectary depth (Fig. 2) \citep{Cocucci:2009,Arditti:2012,Nilsson:1988,Miller:1997}.

Sazatornil et al. approach would be most useful for proper tests of coevolutionary hypotheses in hawkmoth/flower assemblages (and plant-animal mutualisms in general): assessing match/mismatch patterns for every possible pairwise interaction among partners within complex webs of interaction where multiple life-history attributes may contribute biological reasons to expect forbidden links. The morphological match hypothesis is not the only mechanism to explain patterns of hawkmoth–plant interactions, where other life-history limitations may operate generating forbidden links, e.g., phenological mismatches (for example in the case of long-distance or elevational migratory hawkmoths), constraints from foraging for oviposition sites \citep{Alarcon:2008}, energetic constraints due to balances of nectar availability/foraging costs \citep{Borrell:2005}, etc.

@@

\bibitem{VizentinBugoni:2014}
Vizentin-Bugoni, J., Maruyama, P.K. \& Sazima, M. (2014) Processes entangling interactions in communities: forbidden links are more important than abundance in a hummingbird-plant network. Proceedings of the Royal Society of London Series B-Biological Sciences, 281, 20132397.

@@

\bibitem{Miller:1997}
Miller, W.E. (1997) Diversity and evolution of tongue length in hawkmoths (Sphingidae). Journal of the Lepidopterists Society, 51, 9–31.

\bibitem{Alarcon:2008}
Alarcón, R., Davidowitz, G. \& Bronstein, J.L. (2008) Nectar usage in a southern Arizona hawkmoth community. Ecological Entomology, 33, 503–509.

\bibitem{Borrell:2005}
Borrell, B. (2005) Long tongues and loose niches: Evolution of euglossine bees and their nectar flowers. Biotropica, 37, 664–669.

@@

\begin{figure}[h!]
  \caption{Morphological mismatches set important biological constraints for size-limited foragers, including e.g., predators, pollinators, and frugivores. In plant-animal mutualisms, a morphological mismatch between partners sets size limits that filter out a range of phenotypes that otherwise could eventually interact. Other reasons for forbidden links include, e.g., phenological differences \citep{BasJor:2014}. Thus, a number of the potential interactions that could take place in a given mutualistic assemblage simply cannot occur because of biological reasons: these are forbidden interactions. Photo: Andrea Cocucci. An sphingid moth, \textit{Agrius cingulata}, visiting a flower of \textit{Bauhinia mollis} (Fabaceae), Las Yungas, Argentina.}
  \label{Fig1}
  \begin{center}
    \includegraphics[width=14cm]{Fig1}
  \end{center}
\end{figure}

\begin{figure}[h!]
  \caption{The mechanistic basis of morphological mismatches in hawkmoth-flower interactions. Modified and redrawn from \citep{Arditti:2012}.}
  \label{Fig2}
  \begin{center}
    \includegraphics[width=14cm]{Fig2}
  \end{center}
\end{figure}
%---------------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% MS NOTES
\begin{comment}
Arditti et al. Fig 11 legend:
Figure 11. Nectar: sugar content and height of column, proboscis length and coevolution. A, correlation between spur length and extracted nectar volume (modified from Wasserthal, 1997 by the removal of data about species other than Angraecum sesquipedale and the addition of the five lines of text at the base of the figure). B, correlation between height of nectar column and nectar volume measured by extraction and injection (modified from Wasserthal, 1997 by the addition of the two lines of text which start with ‘Mean’). C, comparison between Darwin’s ‘coevolution race’ and Wasserthal’s ‘pollinator shift’ models. In the ‘coevolution race’ model (A) the race is between increasing lengths of spurs and proboscises. The ‘pollination shift’ model (B) involves the recruitment by long-spurred angraecoid orchids of pollinators which are generalist feeders and have proboscises of different lengths. These pollinators are substituted gradually. When spurs enlarge beyond a certain length due to evolutionary pressure by the primary visitors flowers can be exploited (i.e. nectar can be taken from them) by illegitimate visitors with longer proboscises (*). This has been observed in interactions between Xanthopan morganii praedicta and Coelonia solani with Angraecum compactum. Increased selective pressure is exerted by the existence of moth species with long proboscises. Flowers become deceptive, but can still be pollinated when spurs become too long for the primary pollinator to reach the nectar. Pollination is impossible when the proboscis is longer than the spurs because the pollinaria are attached further from the base of the proboscis. When this happens the pollinaria are scratched away by the forelegs when the proboscis is rolled to a loose spiral. If the proboscis is shorter than the spur, transfer of the pollinaria is possible as long as the proboscis can get in contact with the sexual organs of the orchid. This occurs in other angrecoid orchids. Explanation of symbols: *, illegitimate visitor with a long proboscis which exploits flowers; black moth, orchid pollinator; grey moth, non-pollinating visitor; white moth, a moth incapable of pollinating an orchid (modified from Wasserthal, 1997 by moving and adding labels). D, correlation between position of fully inserted proboscis and time of insertion, stay and withdrawal (modified from Wasserthal, 1997 by the removal of data not pertaining to Angraecum sesquipedale). E, Nectar accessibility in Angraecum sesquipedale spurs. a, moth with an average spur length of 22 cm can obtain about 50 mL nectar from a spur of average length of 33.3 cm and an average nectar volume of 165 ml. b, a spur 43 cm long could offer nectar to a moth with a 22-cm-long proboscis only if it contains more than 240 mL solution. C, small volumes of nectar can be exploited if the spur is 27 cm long (Wasserthal, 1997).
